---
title: "Indian Food Orders"
output: rmarkdown::html_vignette
#fig_width: 6
#fig_height: 7
vignette: >
  %\VignetteIndexEntry{Indian Food Orders}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stringr)
library(dplyr)
library(ggplot2)
library(plotly)
library(apply303)
```

```{r, set-fig-size}
knitr::opts_chunk$set(fig.width=8, fig.height=5) 
```


## Visualization

```{r, boxplot of average price of meat/veg dishes}

box <- ggplot(data=name_and_quant, mapping=aes(x=Meat.Veg, y=Product.Price, color=Meat.Veg)) +
  scale_colour_manual(values = c("tomato3","darkgreen")) +
  theme_bw() + 
  ggtitle("Price Distributions for Meat & Vegetable Dishes") +
  xlab("Type of Dish") +
  ylab("Price") +
  geom_boxplot()
```

``` {r}
ggplotly(box)
```

```{r, plot visualization}
#name_and_quant$

p <- name_and_quant %>%
  ggplot( aes(Product.Price, Total.Quantity, color=Meat.Veg, label=Item.Name) ) +
  scale_colour_manual(values = c("tomato3","darkgreen")) +
  geom_jitter(width=0.15) +
  theme_bw() + 
  ggtitle("Items' Number of Orders by Price") +
  xlab("Item Price") +
  ylab("Total Number of Orders")
```


```{r}
ggplotly(p)
```


### Background Information
The item price is probably in pounds, since the data comes from a restaurant in London. I'm more interested in prices relative to each other than the prices themselves.  

### Description of data source
This dataset is from <https://www.kaggle.com/henslersoftware/19560-indian-takeaway-orders>. The set used has ~74000 rows containing information about an Indian restaurant's order history from 01-09-2015 to 12-07-2019.  

Each row represents one order of one item. The columns included are order number, date ordered, item name, item price, quantity of item ordered, and total products in order.  

### References/citations
omg, i love stackoverflow! stackoverflow is my life...  

### Reflections on project...
**What ideas/suggestions from Claus Wilke helped shape your visualization?**  
Wilke's scatterplot of birds' bill length against their skull size-- with color indicating the birds' sex -- gave me the idea to differentiate between meat/non-meat dishes with color. As a sometime vegetarian, I'm interested in comparing the price and popularity of these two groups!  
  
**Is there anything more you wish you could do with this data?**   
YES. I wish I could do cooler things with it.  
I'm still a noob when it comes to graphics and visualizations. This source had data for a whole other restaurant, and I wish I could have compared the two venues somehow. I also wish I could have made my graph look cooler!  
Also, I wish I knew what all the names of the dishes meant. I'm not super familiar with Indian food, so it's entirely possible I missed some meat dishes because I didn't know what words to look for.  
AND FINALLY! I wish I could have gotten my tag_as_meat() function working. Because of time constraints, I ended up using repetitive code to check for each individual meat word. :'(  
  
**What were the most interesting or frustrating technical aspects of doing this?**   
The most interesting aspect was deciding which comparisons I wanted to make, and how I would represent them visually.  
The most frustrating aspect was definitely wrangling the data. Writing an example row from the "end goal" dataset helped... but getting there took quite the struggle!  
